\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{float}
\usepackage{verbatim}
\usepackage{amsthm}
\usepackage[shortlabels]{enumitem}
\renewcommand{\baselinestretch}{1.5}
\newcommand\F{\mathcal{F}}
\newcommand\lb{\left\lbrace}
\newcommand\rb{\right\rbrace}
\newcommand\w{\omega}
\newcommand\Q{\mathbb{Q}}
\newcommand\R{\mathbb{R}}
\newcommand\N{\mathbb{N}}
\newcommand\st{\text{ such that }}
\newcommand\sumOfSeries{\sum_{n = 0}^{\infty}}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{note}{Note}
\newtheorem{proposition}{Proposition}
\parindent 0ex
\begin{document}
\title{Mathematics Year I, Analysis I Term 1 \\ Theorems, propositions. } 
\date{\today}
\author{Szymon Kubica} 
\maketitle

\section{Order Axioms}
    \[ 1. \forall x \in \Q \text{ exactly one of the following holds: } \\ x > 0 \text{ or } x = 0 \text{ or } -x > 0 \text{ (Trichotomy axiom)} \]
    \[ 2. \forall x \in \Q \exists n \in \N \text{ such that } n > x \text{ (Archimedean axiom)}\]
\section{Decimals}
We define an eventually periodic decimal $ a_0.a_1...a_i\overline{a_{i + 1}a_{i + 2}...a_j}$ for $a_0 \in \N$, $a_{i > 0} \in \{0, 1, ..., 9\}$
as the rational number
\[ a_0 + \frac{a_1}{10} + \frac{a_2}{100} + ... + \frac{a_i}{10^{i}} + \left(\frac{a_{i + 1}a_{i + 2}...a_j}{10^{j}}\right) \left(\frac{1}{1 - 10^{i - j}}\right)\]

\begin{theorem}
    Any $ x \in \Q $ is equal to an eventually periodic decimal expansion: \\ $ x =  a_0.a_1...a_i\overline{a_{i + 1}a_{i + 2}...a_j}$ for $a_0 \in \N$, $a_{i > 0} \in \{0, 1, ..., 9\}. $
\end{theorem}

\section{The Completeness Axiom}

\begin{definition}
        Suppose $\emptyset \neq S \subset \R $ is bounded above. We define $ x \in \R $ to be the \textbf{supremum} of $S$ iff:
        \begin{itemize}
            \item $ X $ is an upper bound for $ S $ (i.e. $ x \geq s \forall s \in S $), 
            \item $ x \leq y $ for any $ y $ which is an upper bound for S ($ y \geq s \, \forall s \in S \implies x \leq y $).
        \end{itemize}

\end{definition}

\section{Dedekind cuts}

\begin{definition}
    A nonempty subset $ S \in \Q $ is a Dedekind cut if it satisfies the following properties: 
    \begin{itemize}
        \item If $ s \in S $ and $ s > t \in \Q $ then $ t \in S $ (S is a semi-infinite interval to the left).
        \item $ S $ is bounded above but has no maximum.
    \end{itemize}
\end{definition}

\section{Sequences}

\begin{definition}
    $ a_n \to a $ as $ n \to \infty $ iff $ \forall \epsilon > 0 \; \exists N \in \N $ such that $\forall n \geq N$, $|a_n - a| < \epsilon$.
\end{definition}

\begin{note}
    It is important to remember that $ N $ can depend on $ \epsilon $.
\end{note}

\begin{definition}
    A sequence $ a_n $ converges iff $\exists a \in \R \text{ such that } \forall \: \epsilon \; \exists \: N \in \N \text{ such that } \forall n \geq N \; |a_n - a| < \epsilon$.
\end{definition}

\begin{definition}
    A sequence $ a_n $ diverges iff $\forall a \in \R \; \exists \: \epsilon > 0 \text{ s.t. } \; \forall \: N \in \N \; \exists n \geq N \text{ such that } |a_n - a| \geq \epsilon$.
\end{definition}

\begin{theorem}
    Limits are unique. $ a_n \to a \land a_n \to b \implies a = b$.
\end{theorem}

\begin{theorem}
    If $(a_n)$ is bounded above and monotonically increasing then $ a_n $ converges to \\ $ a := sup\{a_i | i \in \N \} $. We write $ a_n \uparrow a $. 
\end{theorem}

\begin{definition}
    $ (a_n)_{n \geq 1} $ is called a Cauchy sequence iff: 
    \[ \forall \: \epsilon > 0 \; \exists \; N \in \N \st \forall \: n, m \geq N \; |a_n - a_m| < \epsilon. \]
\end{definition}

\begin{theorem}
    If $ (a_n) $ is a Cauchy sequence of real numbers then $ a_n $ converges.
\end{theorem}

\section{Subsequences}

\begin{theorem}[Bolzano-Weierstrass]
    If $ (a_n) $ is a bounded sequence of real numbers then it has a convergent subsequence.
\end{theorem}

\begin{definition}
    We say $ a_n \to +\infty $ if and only if 
    \[ \forall R > 0 \; \exists N \in \N \st \forall \; n \geq N a_n > R\] 
\end{definition}

\section{Series}

\begin{definition}
    The sequence of partial sums $ (s_n) $ of a series is given by:
    \[ s_n = \sum_{i=1}^n a_i.\]
\end{definition}

\begin{definition}
    We say that the series $ \sum a_n $ converges to $ A \in \R $ if and only if the sequence of partial sums converges to $ A $:
    \[ \sum_{n = 1}^{\infty} a_n = A \iff s_n \to A \]
\end{definition}

\begin{theorem}
    $ \sumOfSeries a_n $ is convergent $ \implies a_n \to 0$.
\end{theorem}

\begin{proposition}
    Suppose $a_n \geq 0 \; \forall n $ (i.e. the sequence of partial sums is monotonically increasing), then the following facts are true:
    \begin{enumerate}
        \item $ \sumOfSeries a_n $ converges iff. $ (s_n) $ is bounded above.
        \item Similarly $ \sumOfSeries a_n \to +\infty$ iff. $ (s_n) $ is unbounded. 
    \end{enumerate}
\end{proposition}

\begin{theorem}[Comparison Test]
   If $ 0 \leq a_n \leq b_n \; \forall n $ and $ \sum b_n $ converges then $ \sum a_n $ converges. What is more $ 0 \leq \sumOfSeries a_n \leq \sumOfSeries b_n $.
\end{theorem}

\section{Absolute Convergence}

\begin{theorem}
    Let $ (a_n)_{n \geq 0} $ be a real or complex sequence. If $ \sum a_n $ is absolutely convergent then it is also convergent.
\end{theorem}

\begin{theorem}[Comparison II (Sandwich Test)]
   Suppose $ c_n \leq a_n \leq b_n \forall n $ and $ \sum c_n, \; \sum b_n $ are both convergent. Then $ \sum a_n $ is convergent. 
\end{theorem}

\begin{theorem}[Comparison III]
    If $ \frac{a_n}{b_n} \to L \in \R $ and $ \sum b_n $ is absolutely convergent, then $ \sum a_n $ is absolutely convergent.
\end{theorem}

\begin{theorem}[Alternating Series Test]
    Suppose $ a_n $ is alternating with $ |a_n| \downarrow 0 $. Then $ \sum a_n $ converges. 
\end{theorem}

\begin{theorem}[Ratio Test]
   If $ a_n $ is a sequence such that $ \left|\frac{a_{n + 1}}{a_n} \right| \to r < 1 $, then $ \sum a_n $ is absolutely convergent.
\end{theorem}

\section{Rearrangement of Series}

\begin{theorem}
    $ \sum a_n $ is absolutely convergent $ \iff (1) \land (2) \implies (3) \land (4), $ where
    \begin{enumerate}[(1)]
        \item $ \sum_{a_n \geq 0} a_n $ is convergent (to A say),
        \item $ \sum_{a_n < 0} a_n $ is convergent (to B say),
        \item $ \sum a_n = A + B $, 
        \item $ \sum b_m = A + B $, where $ (b_m) $ is any rearrangement of $ (a_n) $.
    \end{enumerate}
\end{theorem}

\section{Power Series} 

Let $ [0, \infty] $ denote the set $ [0, \infty) \cup \{+\infty\} $.

\begin{theorem}[Radius of Convergence]
   Fix a real or complex series $ (a_n) $ and consider the series $ \sum a_n \, z^n \text{ for} \in \mathbb{C} $. Then $ \exists R \in [0, \infty] \st $
   \begin{itemize}
       \item $ |z| < R \implies \sum a_n \, z^n $ is absolutely convergent, 
       \item $ |z| > R \implies \sum a_n \, z^n $ is divergent.
   \end{itemize}
\end{theorem}

\section{Products of Series}

\begin{definition}
    The Cauchy Product of two series $ \sum a_n $ and $ \sum b_n $ is defined as the series $ \sum c_n $ where $ c_n := \sumOfSeries a_i b_{n - i} $
\end{definition}

\begin{theorem}[Cauchy Product]
    If $ \sum a_n $ and $ \sum b_n $ are absolutely convergent, then their Cauchy product $ \sum c_n $ is absolutely convergent to $ \left(\sum a_n \right) \cdot \left(\sum b_n\right) $
\end{theorem}

\section{Exponential Power Series}

\begin{definition}[Exponential Series]
   For any $ z \in \mathbb{C} $ we set 
   \[ E(z) = \sumOfSeries{\frac{z^n}{n!}} \] 
\end{definition}

\begin{proposition}
    $ E(x) $ has the following properties for $ x \in \R $:
    \begin{enumerate}
        \item $ \forall x \in \R E(x) > 0 $,
        \item $ x \geq 0 \implies E(x) \geq 1 $ and $ x < 0 \implies E(x) < 1 $,
        \item $ E(x) $ is strictly increasing for $ x \in \R $, 
        \item $ |E(x) - 1| \leq \frac{|x|}{1 - |x|} $ for $ |x| < 1 $
    \end{enumerate}
\end{proposition}

\section{Continuity} 

\begin{definition}
    Fix a function $ f: \R \to \R $ and points $ a, b \in \R $.
    
    We say that $ f(x) \to b \text{ as } x \to a $ (or $ \lim_{x \to a} f(x) = b $) if and only if
    \[ \forall \, \epsilon > 0 \; \exists \, \delta > 0 \st |x - a| < \delta \implies |f(x) - b| < \epsilon\]
\end{definition}

\begin{theorem}
    $ f : \R \to \R $ is continuous at $ a \in \R $ if and only if 
    \[ \forall \, \epsilon > 0 \; \exists \, \delta > 0 \st |x - a| < \delta \implies |f(x) - f(a)| < \epsilon\]
\end{theorem}

\begin{theorem}[Sequential Continuity]
   $ f : \R \to \R $ is continuous at $ a \in \R $ if and only if  
   
   $ f(x_n) \to f(a) \; \forall \text{ sequences } x_n \to a.$ 
\end{theorem}
\end{document}
